Make manuscript figures

### 2022-06-23 scripts/R/make_manuscript_figures.rmd
add pdfs for all but gwas figures

shape_legend <- get_legend(rmse_plot + guides(fill = "none") + theme(legend.position = "bottom"))
top_row <- plot_grid(NULL, rmse_plot + guides(shape = "none"), rel_widths = c(1.03, 3), labels = c("", "A"))
png(filename = "figures/simulation_results.png", width = linewidth, height = height, unit = "cm", res = 300)
plot_grid(
        top_row, 
        tpr_plot + guides(shape = "none"), 
        shape_legend, 
        rel_heights = c(1, 1, 0.1),
        align = "v", axis = "tb", nrow = 3, 
        labels = c("", "B", "")
)
dev.off()
```

@@

ggplot(data = tip_pair_data_to_plot, aes(x = factor(dist_decile_rank), y = correlation)) +
        geom_boxplot() + 
        facet_grid(Heritability ~ `Selection strength`, labeller = label_both) + 
        labs(x = "Tree distance decile", y = "Pearson correlation in trait value") + 
        shared_theme
ggsave(filename = "figures/tip_trait_correlation.png", width = linewidth, height = height * 2/3, unit = "cm")

@@

# Arrange plots together
top_row <- plot_grid(
        lo_h2_tree + theme(legend.position = "none"),
        hi_h2_tree + theme(legend.position = "none"),
        labels = c("A", "B"),
        nrow = 1
)
plot_grid(top_row, get_legend(lo_h2_tree),
          p1,
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(1, 1.5),
          rel_widths = c(1, 0.2),
          labels = c("", "", "C"))
ggsave(filename = paste(FIGDIR, "example_simulation_trait_values.png", sep = "/"),
      width = linewidth, height = height, unit = "cm")
```

@@

png(
        filename = paste(FIGDIR, "gwas_results.png", sep = "/"),
        width = linewidth, height = height, unit = "cm", res = 300)
plot_grid(aligned_plots[[1]], aligned_plots[[2]], nrow = 2, labels = c("A", "B"))
dev.off()
```

@@

# Calculate tree distances
tree_dists <- dist.topo(trees, method = "PH85")
```

>>>>

shape_legend <- get_legend(rmse_plot + guides(fill = "none") + theme(legend.position = "bottom"))
top_row <- plot_grid(NULL, rmse_plot + guides(shape = "none"), rel_widths = c(1.03, 3), labels = c("", "A"))

plot_grid(
        top_row, 
        tpr_plot + guides(shape = "none"), 
        shape_legend, 
        rel_heights = c(1, 1, 0.1),
        align = "v", axis = "tb", nrow = 3, 
        labels = c("", "B", "")
)
ggsave(filename = "figures/simulation_results.pdf", width = linewidth, height = height, unit = "cm")
```

@@

ggplot(data = tip_pair_data_to_plot, aes(x = factor(dist_decile_rank), y = correlation)) +
        geom_boxplot() + 
        facet_grid(Heritability ~ `Selection strength`, labeller = label_both) + 
        labs(x = "Tree distance decile", y = "Pearson correlation in trait value") + 
        shared_theme
ggsave(filename = "figures/tip_trait_correlation.pdf", width = linewidth, height = height * 2/3, unit = "cm")

@@

# Arrange plots together
top_row <- plot_grid(
        lo_h2_tree + theme(legend.position = "none"),
        hi_h2_tree + theme(legend.position = "none"),
        labels = c("A", "B"),
        nrow = 1
)
plot_grid(top_row, get_legend(lo_h2_tree),
          p1,
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(1, 1.5),
          rel_widths = c(1, 0.2),
          labels = c("", "", "C"))
ggsave(filename = paste(FIGDIR, "example_simulation_trait_values.pdf", sep = "/"),
      width = linewidth, height = height, unit = "cm")
```

@@

plot_grid(aligned_plots[[1]], aligned_plots[[2]], nrow = 2, labels = c("A", "B"))
ggsave(
        filename = paste(FIGDIR, "gwas_results.pdf", sep = "/"),
        width = linewidth, height = height, unit = "cm"
)
```

@@

# Calculate tree distances
tree_dists <- dist.topo(trees, method = "PH85")
```
Make A. thaliana GWAS figures (here or use scripts/R/plot_manhattan_euler.R)
```{R}
# Load data
print("Loading data")
gwas_results_xanthomonas <- read.delim(
    file = paste(OUTDIR_XANTHAMONAS, "gwas_results.maxmaf.pvals.txt", sep = "/"), 
    sep = "", 
    header = T
)

pt_size <- 1

# Add genome position to data
chr_lengths <- gwas_results_xanthomonas %>%
        group_by(CHROM) %>%
        summarise(chr_len = max(POS))
chr_starts <- chr_lengths %>%
        mutate(CHR_start = cumsum(as.numeric(chr_len)) - chr_len) %>%
        select(-chr_len)
gwas_results_annotated <- left_join(gwas_results_xanthomonas, chr_starts, by = "CHROM")
gwas_results_annotated <- gwas_results_annotated %>%
        arrange(CHROM, POS) %>%
        mutate(BP_position = CHR_start + POS)

# This is maybe not the best way, but makes sure tick marks and labels are at the center of each chromosome
x_axis_ticks <- chr_starts
max_BP_position <- max(gwas_results_annotated[gwas_results_annotated$CHROM == 5, "BP_position"])
x_axis_ticks <- rbind(
        x_axis_ticks,
        data.frame(
                CHROM = c(6),
                CHR_start = c(max_BP_position)))
x_axis_ticks$midpoint <- x_axis_ticks$CHR_start + (lead(x_axis_ticks$CHR_start) - x_axis_ticks$CHR_start)/2

# Make comparative GWAS overview plot
print("Making plot")
bonferroni_signifiance_threshold <- 0.05 / nrow(gwas_results_annotated)
overview_comparison <- ggplot(
        data = results_long,
        aes(x = BP_position, y = -log10(P))) +
        geom_point(aes(color = CHROM %% 2 == 0), size = pt_size) +
        scale_color_manual(values = c("grey", "dark grey")) +
        scale_x_continuous(
                breaks = x_axis_ticks$midpoint,
                labels = x_axis_ticks$CHROM,
                expand = c(0.01, 0.01)) +
        scale_y_continuous(limits = c(0, 16), expand = c(0, 0)) +
        labs(x = "Chromosome", y = expression('-Log'[10]*'(p)')) +
        geom_hline(
                yintercept = -log10(bonferroni_signifiance_threshold),
                linetype = "dashed") +
        shared_theme +
        theme(
                panel.grid.major.x = element_blank(),
                panel.grid.minor.x = element_blank(),
                legend.position = "none"
        ) +
        facet_grid(. ~ gwas_type)

print("Saving plot")
ggsave(
        plot = overview_comparison,
        filename = paste(FIGDIR, "gwas_results_xanthomonas.pdf", sep = "/"),
        width = linewidth, height = height / 2, unit = "cm"
)
```
